\chapter{Ethic checklist}
\section{Ethics and professional considerations}

This project does not involve direct human participant, while uses personal data listed bellow:
\begin{itemize}
	\item NSCLC-Radiomics\cite{clark_cancer_2013} \cite{aerts_decoding_2014} from the Cancer Imaging Archive.\\
	Download link: \textit{https://wiki.cancerimagingarchive.net/display/Public/NSCLC-Radiomics}
	\item MSD Lung Cancer Data from Medical Segmentation Decathlon\cite{DBLP:journals/corr/abs-1902-09063}.\\
	Download link: \textit{http://medicaldecathlon.com/}
	\item Cov Segmentation Benchmark \cite{COVID-19-CT-Seg-Dataset}: Available on GitHub for download, collected by the \textit{Coronacases Initiative} and \textit{Radiopaedia} \\
	Download link: \textit{https://github.com/JunMa11/COVID-19-CT-Seg-Benchmark}
	\item MosMed dataset: \textit{https://mosmed.ai/en/}
	
\end{itemize}
 This project only uses the CT scans offered officially while also offers anonymized data about the age and survival of patients. Moreover, although the dataset is officially public, we made sure that we had all the necessary authorizations to use it, and we strictly follow the BCS code and IET rules of conduct. The ethic checklist is list below
\newpage
\begin{longtable}{|p{12cm}|p{1cm}|p{1cm}|}
\endhead

\hline & Yes & No \\ \hline
\rowcolor[HTML]{FFFE65} 
Section 1: HUMAN EMBRYOS/FOETUSES &     &    \\ \hline
Does your project involve Human Embryonic Stem Cells? &     & X  \\ \hline
Does your project involve the use of human embryos?  &     & X  \\ \hline
Does your project involve the use of human foetal tissues / cells?     &     & X  \\ \hline
\rowcolor[HTML]{FFFE65} 
Section 2: HUMANS     &     &    \\ \hline
Does your project involve human participants?    &     & X  \\ \hline
\rowcolor[HTML]{FFFE65} 
Section 3: HUMAN CELLS / TISSUES &     &    \\ \hline
Does your project involve human cells or tissues? (Other than from “Human Embryos/Foetuses” i.e. Section 1)?  &     & X  \\ \hline
\rowcolor[HTML]{FFFE65} 
Section 4: PROTECTION OF PERSONAL DATA  &     &    \\ \hline
Does your project involve personal data collection and/or processing? &     X &   \\ \hline
Does it involve the collection and/or processing of sensitive personal data (e.g. health, sexual lifestyle, ethnicity, political opinion, religious or philosophical conviction)?  &     & X  \\ \hline
Does it involve processing of genetic information? &     & X  \\ \hline
Does it involve tracking or observation of participants? It should be noted that this issue is not limited to surveillance or localization data. It also applies to WAN data such as IP address, MACs, cookies etc.  &     & X  \\ \hline
Does your project involve further processing of previously collected personal data (secondary use)? For example Does your project involve merging existing data sets?                     &  X   &   \\ \hline
\rowcolor[HTML]{FFFE65} 
Section 5: ANIMALS                                              &     &    \\ \hline
Does your project involve animals?                             &     & X  \\ \hline
\rowcolor[HTML]{FFFE65} 
Section 6: DEVELOPING COUNTRIES                                &     &    \\ \hline
Does your project involve developing countries?                 &     & X  \\ \hline
If your project involves low and/or lower-middle income countries, are any benefit-sharing actions planned?            &     & X  \\ \hline
Could the situation in the country put the individuals taking part in the project at risk?                                   &     & X  \\ \hline
\rowcolor[HTML]{FFFE65} 
Section 7: ENVIRONMENTAL PROTECTION AND SAFETY                 &     &    \\ \hline
Does your project involve the use of elements that may cause harm to the environment, animals or plants?                    &     & X  \\ \hline
Does your project deal with endangered fauna and/or flora /protected areas?                                              &     & X  \\ \hline
Does your project involve the use of elements that may cause harm to humans, including project staff?                       &     & X  \\ \hline
Does your project involve other harmful materials or equipment, e.g. high-powered laser systems?                               &     & X  \\ \hline
\rowcolor[HTML]{FFFE65} 
Section 8: DUAL USE                                            &     &    \\ \hline
Does your project have the potential for military applications?  &     & X  \\ \hline
Does your project have an exclusive civilian application focus?  &     & X  \\ \hline
Will your project use or produce goods or information that will require export licenses in accordance with legislation on dual use items?  &     & X  \\ \hline
Does your project affect current standards in military ethics – e.g., global ban on weapons of mass destruction, issues of proportionality, discrimination of combatants and accountability in drone and autonomous robotics developments, incendiary or laser weapons? &     & X  \\ \hline
\rowcolor[HTML]{FFFE65} 
Section 9: MISUSE  &     &    \\ \hline
Does your project have the potential for malevolent/criminal/terrorist abuse?   &     & X  \\ \hline
Does your project involve information on/or the use of biological-, chemical-, nuclear/radiological-security sensitive materials and explosives, and means of their delivery? &     & X  \\ \hline
Does your project involve the development of technologies or the creation of information that could have severe negative impacts on human rights standards (e.g. privacy, stigmatization, discrimination), if misapplied?   &     & X  \\ \hline
Does your project have the potential for terrorist or criminal abuse e.g. infrastructural vulnerability studies, cybersecurity related project?  &     & X  \\ \hline

\rowcolor[HTML]{FFFE65} 
SECTION 10: LEGAL ISSUES &     &    \\ \hline
Will your project use or produce software for which there are copyright licensing implications?   &     & X  \\ \hline
Will your project use or produce goods or information for which there are data protection, or other legal implications?   &    &  X  \\ \hline

\rowcolor[HTML]{FFFE65} 
SECTION 11: OTHER ETHICS ISSUES  &     &    \\ \hline
Are there any other ethics issues that should be taken into consideration?  &    & X  \\ \hline

\caption{Ethics checklist \label{tab:ethics_checklist}} \\

\end{longtable}
